\textsc{Rils}-\textsc{Rols} : Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-11-07 paper_resources/doc/paper.tex
Section 3: start to polish

	\section{The proposed method}\label{sec:rils}
		\fxnote{TODO: needs for extension...}
	Before we give details on our \textsc{Rils}-\textsc{Rols}  method for solving SR, we will explain the basics of two main techniques incorporated into our algorithm. These are ILS meta-heuristic and OLS methods.

@@

	An initial solution may be generated randomly or by using a greedy heuristic, which is afterwards, improved by local search. At each iteration, ILS applies three steps. First, the current incumbent solution is perturbed -- it is partially randomized. Next, the perturbed solution is improved with LS procedure. Thirdly, the LS outcome is thereafter compared to the incumbent solution and the search us possibly moved to the new solution, with accordance to the chosen acceptance criterion. Sometimes, ILS incorporates a mechanism of tabu list, which prevents the search getting back to already visited solutions.

@@

	Thus, we get the system of equations: 
	\begin{align*}
		% &\sum -2X_i (\tilde{y}_i - y_i )  = 0 \\
		& -2X_1 (y_1 - \tilde{y}_1)  = 0 \\
		& \vdots \\
		& -2X_d (y_d - \tilde{y}_d)  = 0 \\
		&\sum -2  (y_i - \tilde{y}_i) = 0.
	\end{align*}
	%The above system can be transformed to 
	%\begin{align*}
	%	 & \sum y_i \cdot x_i   = b\sum x_i \cdot x_i  +  k \cdot \sum x_i \\
	%	 & \sum y_i  = k \sum x_i + b \cdot d. 
	%  \end{align*}
By solving this system of $(d+1)$ equations, one can obtain vector of coefficients $k=(k_1, ..., k_d)$ and intercept $b$. %For example, in order to calculate coefficient $k_i$, the following system of equations is 
\fxnote{TODO: Aca -- ovde je pisalo da je to sistem sa dve jednacine i dve nepoznate k i b -- medjutim, k je vektor. Ako mozes dopisi jos nesto, tipa koliko je podataka potrebno i slicno -- mozda veremenska slozenost.) }%https://towardsdatascience.com/understanding-the-ols-method-for-simple-linear-regression-e0a4e8f692cc
\subsection{\textsc{Rils}-\textsc{Rols}  method}
Now we will explain the proposed \textsc{Rils}-\textsc{Rols}  method in detail. The overall method scheme is given in Algorithm~\ref{alg:rilsrols}.

>>>>

	\section{The proposed method}\label{sec:rils}

	Before we give details on our \textsc{Rils}-\textsc{Rols}  method for solving SR, we will explain the basics of two main techniques incorporated into our algorithm. These are ILS meta-heuristic and OLS methods.

@@

	An initial solution may be generated randomly or by using a greedy heuristic, which is afterwards, improved by local search. At each iteration, ILS applies three steps. First, the current incumbent solution is perturbed -- it is partially randomized. Next, the perturbed solution is improved by a LS procedure. Thirdly, the LS outcome is thereafter compared to the incumbent solution and the search us possibly moved to the new solution, with accordance to the chosen acceptance criterion. Sometimes, ILS incorporates a mechanism of tabu list, which prevents the search getting back to already visited solutions.

@@

	Thus, we get the system of equations: 
	\begin{align*}
		% &\sum -2X_i (\tilde{y}_i - y_i )  = 0 \\
		& -2X_1 (y_1 - \tilde{y}_1)  = 0 \\
		& \vdots \\
		& -2X_d (y_d - \tilde{y}_d)  = 0 \\
		&\sum -2  (y_i - \tilde{y}_i) = 0.
	\end{align*}
	%The above system can be transformed to 
	%\begin{align*}
	%	 & \sum y_i \cdot x_i   = b\sum x_i \cdot x_i  +  k \cdot \sum x_i \\
	%	 & \sum y_i  = k \sum x_i + b \cdot d. 
	%  \end{align*}
By solving this system of $(d+1)$ equations, one can obtain vector of coefficients $k=(k_1, ..., k_d)$ and intercept $b$. %For example, in order to calculate coefficient $k_i$, the following system of equations is 
%\fxnote{TODO: Aca -- ovde je pisalo da je to sistem sa dve jednacine i dve nepoznate k i b -- medjutim, k je vektor. Ako mozes dopisi jos nesto, tipa koliko je podataka potrebno i slicno -- mozda veremenska slozenost.) }%https://towardsdatascience.com/understanding-the-ols-method-for-simple-linear-regression-e0a4e8f692cc
\subsection{\textsc{Rils}-\textsc{Rols}  method}
Now we will explain the proposed \textsc{Rils}-\textsc{Rols}  method in detail. The overall method scheme is given in Algorithm~\ref{alg:rilsrols}.  \fxnote{Marko: došao dovde!}
